---
title: 'Class 06: Scarping One or More Web Pages'
author: "Alex Harris"
date: "2026-02-23"
output: 
  html_document:
    toc: TRUE
    toc_float: TRUE 
    number_sections: TRUE
    code_download: TRUE
    code_folding: show
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Demo: Scraping MU ISA Courses and Descs

In this demo, I am scraping the course title and course description from [MU's ISA Course Bulletin](https://bulletin.miamioh.edu/courses-instruction/isa/).

## Step Up
```{r scarpe_isa}
# step 0: can I scape this based on the robots.txt
robotstxt::paths_allowed(paths = "https://bulletin.miamioh.edu/courses-instruction/isa/")

# Step 1: get the raw HTML of the page into R (save this step so we don't overload the Miami servers)

mu_webpage = rvest::read_html("https://bulletin.miamioh.edu/courses-instruction/isa/")

# steps 2 and 3: we will do this separetnly for the titles and course descriptions 
## div, p, strong found from highlighting heading you want, inspecting and looking at the column beneath the code
mu_webpage |> 
  rvest::html_elements("div.courseblock > p.courseblocktitle > strong") |>
  rvest::html_text2() -> course_titles_a
```

## Finding the course titles
```{r finding_course_titles}
# alternatively, let us work our way through what the inspect gives us 
# highlighted ISA 401 course title on the website -> went in inspect -> went to copy selector to get the #sc... 
# if you anted to work your way through this, you will have to drop the n-th child 
course_titles_b = 
  mu_webpage |> 
  rvest::html_elements("#sc_sccoursedescs > div:nth-child(23) > p.courseblocktitle > strong") |>
  rvest::html_text2() 

# From the selector gadget (chrome extension), it seems that we have two options
course_titles_c = 
  mu_webpage |> 
  rvest::html_elements("strong") |>
  rvest::html_text2() 

# it also implied that I can potentially get this using p strong
## command enter to run one section at a time if you dont want to run the whole chunk
course_titles_d = 
  mu_webpage |> 
  rvest::html_elements("p strong") |>
  rvest::html_text2() 

```

## Finding the course descriptions
```{r finding_course_desc}
# get the course descriptions 
course_descriptions_a = 
  mu_webpage |> 
  rvest::html_elements(".courseblockdesc") |>
  rvest::html_text2() 

course_descriptions_b = 
  mu_webpage |> 
  rvest::html_elements("div#sc_sccoursedescs > div.courseblock > p.courseblockdesc") |>
  rvest::html_text2() 

# what happens we we use div p
  mu_webpage |> 
  rvest::html_elements("div p") |>
  rvest::html_text2() -> temp_output
  
temp_output = temp_output[1:100]  

#f1 to get help description
course_titles = temp_output[ seq(from = 1, to = 100, by = 2)]
course_desc = temp_output[ seq(from = 2, to = 100, by = 2)]

df = data.frame(title = course_titles, desc = course_desc)
```


# Creating out Own Function to Scape FSB Pages
```{r my_function}
# https://bulletin.miamioh.edu/courses-instruction/isa/
# my expecation is the only things that needs to change is isa
# in one of three ways: 
# (a) https://bulletin.miamioh.edu/courses-instruction/ remain fixed : isa/
# (b) https://bulletin.miamioh.edu/courses-instruction what changes is /isa/
# (c) change the entire URL each time

# based on the first vote inc lass, we will do b
scrape_fsb = function(suffix = 'isa'){
  bulletin_url = paste0(
    "https://bulletin.miamioh.edu/courses-instruction", "/", suffix, '/'
  )
  
  # using same object names from before allows me to not change the subsequent code at all
  # BUT: INPUT URL HAS TO BE A R OBJECT THAT CHANGES
  mu_webpage = rvest::read_html(bulletin_url)
  
  # PREVIOUS CODE THAT WE ESTABKLE THAT IT WORKED FOR ISA
  # what happens we we use div p
  mu_webpage |> 
    rvest::html_elements("div p") |>
    rvest::html_text2() -> temp_output
  
  temp_output = temp_output[1:100]  
  
  #f1 to get help description
  course_titles = temp_output[ seq(from = 1, to = 100, by = 2)]
  course_desc = temp_output[ seq(from = 2, to = 100, by = 2)]
  
  df = data.frame(title = course_titles, desc = course_desc)
  
  Sys.sleep(2) # being nice and not overwhelming MU servers
  
  # you have to specify wat you are returning (either by not saving data.frame output into a R object) or by using explicitly return(df)
  return(df)
}
  
```

## Test our custom function for marketing 
```{r implement_fun}
mkt_df = scrape_fsb(suffix='mkt')
```


# Use our Custom Function for all FSB Courses 
```{r scrape_fsb_courses}

fsb_vec = c('isa', 'mkt', 'fin', 'eco', 'mgt', 'acc', 'esp', 'bus')

fsb_df = data.frame() # container where I store all the courses 
for (name in fsb_vec) {
  df = scrape_fsb(suffix = name)
  
  fsb_df = rbind(fsb_df, df)
}


```

## Use our Function (via `purrr`) 
```{r purrr}
fsb_df_alt = purrr:map_df(
  .x=fsv_vec, .f = scrape_fsb
)
```


```{r scarpe_isa}


# Step 1: get the raw HTML of the page into R (save this step so we don't overload the Miami servers)

mu_webpage = rvest::read_html("https://bulletin.miamioh.edu/courses-instruction/isa/")

# steps 2 and 3: we will do this separetnly for the titles and course descriptions 
## div, p, strong found from highlighting heading you want, inspecting and looking at the column beneath the code
mu_webpage |> 
  rvest::html_elements("div.courseblock > p.courseblocktitle > strong") |>
  rvest::html_text2() -> course_titles_a
```

```{r scrap 25_26}
# step 0: can I scape this based on the robots.txt
robotstxt::paths_allowed(paths = "https://www.planecrashinfo.com/2025/2025.htm")

plane_url = "https://www.planecrashinfo.com/2025/2025.htm"

# Step 1: get the raw HTML of the page into R (save this step so we don't overload the Miami servers)
plane_page = rvest::read_html(plane_url)

# steps 2 and 3: we will do this separately for the titles and course descriptions 
## div, p, strong found from highlighting heading you want, inspecting and looking at the column beneath the code
plane_page |> 
  rvest::html_elements("div > center > table") |>
  rvest::html_table(header = TRUE) |>
  magrittr::extract2(1) -> plane_df
```


## My Own Function
```{r scrape_fn}
scrape_plane = function(plane_url){
  
# Step 1: get the raw HTML of the page into R (save this step so we don't overload the Miami servers)
plane_page = rvest::read_html_live(plane_url)

# steps 2 and 3: we will do this separately for the titles and course descriptions 
## div, p, strong found from highlighting heading you want, inspecting and looking at the column beneath the code
plane_page |> 
  rvest::html_elements("div > center > table") |>
  rvest::html_table(header = TRUE) |>
  magrittr::extract2(1) -> plane_df
  
sys.sleep(10)

return(plane_df)
}
```


## Apply the Function
```{r apply_planes}
plane_urls = paste0(
  "https://www.planecrashinfo.com/", 2025:2026, '/', 2025:2026, '.htm'
  )

plane_df = purrr::map_df(.x = plane_urls, .f = scrape_plane)
```

# Google Examples
```{r}
robotstxt::paths_allowed(paths = "https://www.google.com/about/careers/applications/jobs/results/?q=data%20analyst&page=")

robotstxt:
```

